Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-07-13 ms.tex
Adam changed some wording and re-ordered a few sentences.

\begin{abstract}
Low-temperature L dwarfs exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres. The spectral character of these variations yield insight into the particle sizes and vertical structure of the clouds. Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility. By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth. We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no clear spectral dependence while 2MASS~J1821+1414 varies by up to $\pm$1.5\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths. The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 0.9--2.4~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction from dust particles with a log-normal particle size distribution with a median radius of 0.24 $\mu$m. We detect no statistically significant phase variations with wavelength. The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader variability survey.
\end{abstract}

@@

Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which references stars are simultaneously observed to correct for telluric effects  (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}) can significantly improve the precision of ground-based spectro-photometry. \citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star Corot-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby visual binary companion in a wide (3$\arcsec$) slit. This was sufficient to infer the presence of a cloud/haze layer in Corot-1b via transmission spectroscopy. A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}. In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing it and its L dwarf companion. These studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground.

@@

\begin{figure*}
\centering
	\plottwo{image0835-0819.pdf}{image1821+1414.pdf}
	\label{fig:image1821}
	\vspace{-.9in}
	\caption{2MASS $JHK_s$ three-color images of the fields around our targets {\sha} (left) and {\shb} (right)
	from the IRSA Finderchart service (\url{http://irsa.ipac.caltech.edu/applications/finderchart/}).  Each image is centered on the target, and span a 1$\arcmin\times\arcmin$ field of view oriented with North up and East the left. The comparison stars referred to in the text appear as blue sources in these images.
	For \sha\, we use the comparison star to the left and for \shb\ the lower right.}
	\label{fig:images}
	\vspace{0.17in}
\end{figure*}

This article reports the results of a pilot study adapting these methods to measuring the variability of two L-type dwarfs with nearby visual companions. We describe our target selection process and pilot target properties in Section~\ref{sec:targets}.
In Section~\ref{sec:obs}, we describe our monitoring observations and data reduction procedures to generate relative spectro-photometric time series.
In Section~\ref{sec:analysis}, we analyze these time series using sinusoidal model fits over discrete spectral bands to generate individual light curves and amplitude spectra.
We then fit the variability amplitude spectra with a Mie extinction model for the clouds and constrain the particle size distribution.
We summarize our results in Section~\ref{sec:conclusions}.

@@

We computed brightness temperature spectra from these data as
\begin{equation}
T_{\lambda,surf} = \frac{hc}{k\lambda}\left[\ln\left(1+\frac{2\pi{hc^2}}{F_{\lambda,surf}\lambda^5}\right)\right]^{-1}
\end{equation}
where the surface flux density $F_{\lambda,surf}$ is computed as
\begin{equation}
F_{\lambda,surf} = {\pi}B_{\lambda} = F_{\lambda,obs}\left(\frac{d}{R}\right)^2 = F_{\lambda,abs}\left(\frac{10~{\rm pc}}{R}\right)^2
\end{equation}
$F_{\lambda,obs}$ and $F_{\lambda,abs}$ are the observed and absolute flux densities, $B_\lambda$ is the Planck function, $d$ the source distance and $R$ the source radius.  Both spectra were calibrated to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes \citep{2016MNRAS.455..357S,2016AJ....152...24W}. We adopted radii from the evolutionary models of \citet{2003A&A...402..701B} assuming bolometric luminosities from \citet{2015ApJ...810..158F} for {\sha} and from\footnote{The parameters reported for {\shb} in \citet{2016ApJS..225...10F} are in error, but have been updated here based on a forthcoming erratum (J.\ Faherty, 2017, priv.\ comm.).} \citet{2016ApJS..225...10F} for {\shb} (Table~\ref{tab:bdProp}). Uncertainties in the spectral fluxes, absolute photometric calibration, adopted {\lbol} and radius were propagated by Monte Carlo simulation.  For {\sha} we considered two cases: radii of 0.114--0.137~R$_{\odot}$ for ages of 50--200~Myr, the age range estimated for INT-G sources by \citet{2013ApJ...772...79A}; and radii of 0.088--0.101~R$_{\odot}$ for ages of 0.5--3~Gyr; i.e., a field dwarf age.
For {\shb}, we assumed an lower age limit of 200~Myr based on its field gravity classification, and an upper limit of 700~Myr based on the analysis of \citet{2016MNRAS.455..357S}. The Baraffe et al.\ evolutionary models predict radii of 0.097--0.114~R$_{\odot}$ for these ages and the luminosity of {\shb}.

@@

\begin{deluxetable*}{lccccccccc}
\tablecaption{Observations\label{tab:obsParam}}
\tablewidth{0pt}
\tablehead{
 & \multicolumn{3}{c}{Observation Epoch (UT)} \\
 \cline{2-4}
\colhead{Target} & 
\colhead{Date} & 
\colhead{Start} & 
\colhead{End} & 
\colhead{$N_{int}$} & 
\colhead{$t_{int}$} & 
\colhead{Duration} & 
\colhead{Airmass} & 
\colhead{Reference Star} & 
\colhead{FWHM \@ $H$} \\
 & &  &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Start-End} & & \colhead{(\arcsec)}}
\startdata
{\sha} & 2015-12-31 & 09:35:10 & 14:14:22 & 352 & 60 & 7.47 & 1.59-1.28 & J08354383-0819212 & 0.5 \\
{\shb} & 2016-06-25 & 07:29:31 & 14:57:58 & 363 & 45 & 4.65 & 1.42-2.15 & J18212622+1414064 & 0.5 \\
\enddata
\tablecomments{N$_{int}$ is the number of integrations and t$_{int}$ is the effective integration time for the 32 non-destructive reads up the ramp. The duration is the total time from start to end of the observations including the reset times and overheads. The FWHM is the measured median value of the time series around 1.6$\mu$m.}
\end{deluxetable*}

@@

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
	\label{fig:specphot0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
	\label{fig:specphot1821}
	}
	\caption{Top Panels: Normalized median raw spectra of {\sha} (left) and {\shb} (right) in black, compared with the respective reference stars (blue) and background emission (red; mostly telluric OH emission and thermal background). The areas of higher telluric absorption are visible near 1.4~$\mu$m and 1.8~$\mu$m.  Bottom Panels: Dynamic spectra of each brown dwarf system. The dynamic spectrum for \sha\ shows no significant variability in the spatial or spectral direction whereas \shb\ shows significant repeated modulations with a period near 4 hours.
The variability in \shb\ is prominent at the short wavelengths with a magnitude of ~$\sim$2\% peak-to-trough at short wavelengths but $\lesssim 0.5\%$ toward 2~$\mu$m.}
	\label{fig:specphot}
	\vspace{0.1in}
\end{figure*}

@@

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
	\label{fig:tserPhase0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
	\label{fig:tserPhase1821}
	}
	\caption{Time series for each system with an offset added for clarity.
	Each wavelength bin is labeled on the right side. Changing colors are used to distinguished the light curves with offsets. \sha\ shows relatively flat light curves whereas \shb\ has large amplitude double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.
	Green brackets show regions where telluric absorption can contaminate the time series.}
	\label{fig:tserDetrend}
\end{figure*}

\begin{figure*}
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
	\label{fig:ampspec0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
	\label{fig:ampspec1821}
	}
	\caption{(Top panels) Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no significant variability nor trends with wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
	 The amplitude spectrum for each system is fit a simple Mie scattering model for a log-normal particle size distribution of spherical forsterite grains.
	 \sha\ is consistent with a zero amplitude model which puts no constraints on the particle size distribution.
	 \shb\ is shown with the best fit median particle size of 0.28 $\mu$m grains.
	 In all plots the regions potentially contaminated by telluric absorption are shaded in light green.
	 {\it Bottom Panels:} The time of maximum variation $t_1$ (in hours) is shown for each brown dwarf relative to the reference epoch (JD 2457388.0 and JD 2457565.0 for \sha\ and \shb\ respectively).
	 Neither $t_1$ spectrum shows a clear trend with wavelength indicating no significant spot offsets.
	 For wavelengths with small variability amplitudes, $t_1$ becomes as wide as the prior window $-\tau/2 < t_1 < \tau/2$.}
	\label{fig:ampSpec}
\end{figure*}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_a2_t2.pdf}
\caption{Secondary sinusoidal amplitude ($A_2$) as a function of wavelength for \shb.
As in Figure \ref{fig:ampSpec}, the regions potentially contaminated by telluric absorption are shown in green.
The secondary amplitude $A_2$ shows a gradual decrease as a function of wavelength as with $A_1$, indicative of Mie scattering grains.
{\it Bottom Panel:} The time of maximum variation $t_2$ shows no clear phase shift trend.
The constraints approach the prior $\pm \tau$/4 when no significant variability is detected.
The $A_2$ constraints for \sha\ (not shown) are all consistent with zero.}\label{fig:amp2Spec}
\end{centering}
\end{figure}

@@

Figure \ref{fig:specphot} shows the raw spectra of the two brown dwarfs, their reference spectra and the background spectra.
Neither the reference spectra nor the brown dwarf spectra have any corrections applied for telluric absorption or instrumental spectral response.
The reference stars have significantly bluer spectra than the brown dwarfs, but nonetheless contain the same telluric absorption signatures.
The regions near 1.37~$\mu$m and 1.83~$\mu$m have significantly lower flux due to telluric water vapor absorption.

Figure \ref{fig:specphot} also shows the dynamic spectra, the relative source brightness as a function of wavelength and time.
{\sha} has a dynamic spectra resembling white noise with no significant variations in either spectral or temporal axes at the $\lesssim$0.5\% level.
{\shb}, on the other hand, shows a clear periodic signal that is strongest at the shortest wavelengths and declines in amplitude toward the longest wavelengths. The periodic signal is nearly coincident with the 4.2~hr period measured by \citet{2015ApJ...799..154M}, enabling confirmation that the signal is astrophysical rather than systematic (see \citealt{2016ApJ...826..156S}).
Both sources exhibit some systematic features in the strong telluric absorption bands at 1.4 and 1.8~$\mu$m, likely caused by residual wavelength drifts from flexure and lower signals-to-noise.

@@

As seen in Figure~\ref{fig:tserDetrend}, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particularly in bands $<$1.8~$\mu$m. 
These variations are periodic with ``double-hump'' structures at peak amplitudes around -2.7~hr and +1.3~hr relative to JD 2457565.00.
The amplitude of these variations is strongly wavelength-dependent with $\sim$3.0\% peak-to-trough variations at short 
wavelengths and near-zero amplitude at the longest wavelengths.
A possible difference between the two brown dwarfs is the viewing geometry with \sha\ closer to pole-on and \shb\ closer to equator-on as shown in Table \ref{tab:bdProp}.
Recently, \citet{vos2017viewingGeom} find that there are correlations between variability and color properties as a function of viewing geometry and that equator-on dwarfs show, on average, larger variability amplitudes.

Each of the light curves were fit to a double sinusoidal model:
\begin{equation}\label{eq:cosfit}
\begin{split}
F(t) = \left( A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + 1\right) \\
\times (B t + C + D a(t))
\end{split}
\end{equation}
where $F(t)$ is the flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two terms, $t_1$ and $t_2$ are the time of maximum periodic flux for each cosine term, $\tau$ is period of the variations, $a(t)$ is the airmass as a function of time and $B$, $C$ and $D$ are terms describing the baseline trend.
Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
For \sha\ we use a prior 2.6 $< \tau < $3.6 hr and for \shb\ we use 3.7 $< \tau <$ 4.7 hr.
Each of these ranges are $\pm$0.5 hr from the literature values.
These priors are wide enough they don't drive the constraints on $\tau$ at short wavelengths for \shb\ but narrow enough to ensure that the sinusoidal fits do not just fit the airmass trends with time.
We also restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ and $-\tau/4 < t_2 < \tau/4$ to assure there are no 2$\pi$ degeneracies in the fit.
We do not put any constraints on A$_1$ relative to A$_2$.

Figure \ref{fig:ampSpec} shows the MCMC posterior constraints for periodic amplitudes as a function of wavelength.
For {\sha} (Figure \ref{fig:ampspec0835}) we find at most small amplitude variability ($\lesssim 0.5\%$), marginally significant at 1.7~$\mu$m and 2.1--2.35~$\mu$m, with a flat trend as a function of wavelength.
\shb, on the other hand, shows clear variability with a decreasing trend in amplitude as function of wavelength.
In both cases, we find no statistically significant wavelength dependence on the time of maximum variation $t_1$, and hence no phase variation.
The period of \shb\ is found to be consistent with that of \citet{2015ApJ...799..154M}.
If we optimistically assume all wavelengths are statistically independent, the weighted average rotation period is 4.10 $\pm$ 0.03 hours.

Figure \ref{fig:amp2Spec} shows the posterior constraints on the secondary sinusoidal term.
As with $A_1$, the amplitude spectrum decreases as a function of wavelength, indicating Mie scattering grains and that the higher frequency term is likely just smaller scale cloud structures with similar properties as the longer timescale variability.
As with Figure \ref{fig:ampSpec}, we find no strong phase shift for the second time of maximum variation $t_2$ as a function of wavelength.

The same trend of decreasing variability amplitude for \shb\ was observed by HST's WFC3 grism over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{2015ApJ...798L..13Y}, also shown in Figure \ref{fig:ampspec1821}.
The HST WFC3 maximum over minimum flux spectrum is converted to an amplitude spectrum by assuming that the amplitude is half the difference in maximum and minimum flux, which can be shown to be 
\begin{equation}\label{eq:ampFromRatio}
A  = \frac{f_R - 1}{f_R + 1}
\end{equation}
where $f_R$ is the flux ratio of the maximum over minimum flux.
There is a multiplicative offset of 25\% between the IRTF and WFC3 spectrum because they were taken at different epochs and presumably have different spatial cloud and temperature distributions.
\citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and is consistent with our gradually decreasing slope from 1.1 to 1.7~$\mu$m.

@@

\citet{hiranaka2016subMicronDust} find that the observed spectra of reddened L dwarfs can be explained by extinction from a haze layer of sub-micron forsterite grains.
They find typical mean particle radii of 0.15 to 0.35 $\mu$m for a sample of L dwarf stars.
Our median particle radius of $r$=0.24 $^{+0.05}_{-0.07}$~$\mu$m for \shb\ is consistent with this range and may represent a partially cloudy version of the reddened brown dwarfs in \citet{hiranaka2016subMicronDust} or WISEP J0047+6803.

>>>>

\begin{abstract}
Low-temperature L dwarfs exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres. The spectral character of these variations yield insight into the particle sizes and vertical structure of the clouds. Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility. By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth. We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no clear spectral dependence, while 2MASS~J1821+1414 varies by up to $\pm$1.5\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths. The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 0.9--2.4~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction from dust particles with a log-normal particle size distribution with a median radius of 0.24 $\mu$m. We detect no statistically significant phase variations with wavelength. The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader survey.
\end{abstract}

@@

Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which references stars are simultaneously observed to correct for telluric effects can significantly improve the precision of ground-based spectro-photometry (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}). \citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star Corot-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby visual binary companion in a wide (3$\arcsec$) slit. This was sufficient to infer the presence of a cloud/haze layer in Corot-1b via transmission spectroscopy. A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}. In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing it and its L dwarf companion. These studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground.

@@

\begin{figure*}
\centering
	\plottwo{image0835-0819.pdf}{image1821+1414.pdf}
	\label{fig:image1821}
	\vspace{-.9in}
	\caption{2MASS $JHK_s$ three-color images of the fields around our targets {\sha} (left) and {\shb} (right)
	from the IRSA Finderchart service (\url{http://irsa.ipac.caltech.edu/applications/finderchart/}).  Each image is centered on the target, and span a 1$\arcmin\times$1$\arcmin$ field of view oriented with North up and East the left. The comparison stars referred to in the text appear as blue sources in these images.
	For \sha\, we use the comparison star to the left and for \shb\ to the lower right.}
	\label{fig:images}
	\vspace{0.17in}
\end{figure*}

This article reports the results of a pilot study adapting these methods to measure the variability of two L-type dwarfs with nearby visual companions. We describe our target selection process and pilot target properties in Section~\ref{sec:targets}.
In Section~\ref{sec:obs}, we describe our monitoring observations and data reduction procedures to generate relative spectro-photometric time series.
In Section~\ref{sec:analysis}, we analyze these time series using sinusoidal model fits over discrete spectral bands to generate individual light curves and amplitude spectra.
We then fit the variability amplitude spectra with a Mie extinction model for the clouds and constrain the particle size distribution.
We summarize our results in Section~\ref{sec:conclusions}.

@@

We computed brightness temperature spectra from these data as
\begin{equation}
T_{\lambda,surf} = \frac{hc}{k\lambda}\left[\ln\left(1+\frac{2\pi{hc^2}}{F_{\lambda,surf}\lambda^5}\right)\right]^{-1}
\end{equation}
where the surface flux density $F_{\lambda,surf}$ is computed as
\begin{equation}
F_{\lambda,surf} = {\pi}B_{\lambda} = F_{\lambda,obs}\left(\frac{d}{R}\right)^2 = F_{\lambda,abs}\left(\frac{10~{\rm pc}}{R}\right)^2
\end{equation}
$F_{\lambda,obs}$ and $F_{\lambda,abs}$ are the observed and absolute flux densities, $B_\lambda$ is the Planck function, $d$ the source distance and $R$ the source radius.  Both spectra were calibrated to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes. We adopted radii from the evolutionary models of \citet{2003A&A...402..701B} assuming bolometric luminosities from \citet{2015ApJ...810..158F} for {\sha} and from\footnote{The parameters reported for {\shb} in \citet{2016ApJS..225...10F} are in error, but have been updated here based on a forthcoming erratum (J.\ Faherty, 2017, priv.\ comm.).} \citet{2016ApJS..225...10F} for {\shb} (Table~\ref{tab:bdProp}). Uncertainties in the spectral fluxes, absolute photometric calibration, adopted {\lbol} and radii were propagated by Monte Carlo simulation.  For {\sha} we considered two cases: radii of 0.114--0.137~R$_{\odot}$ for ages of 50--200~Myr, the age range estimated for INT-G sources by \citet{2013ApJ...772...79A}; and radii of 0.088--0.101~R$_{\odot}$ for ages of 0.5--3~Gyr; i.e., a field dwarf age.
For {\shb}, we assumed an lower age limit of 200~Myr based on its field gravity classification, and an upper limit of 700~Myr based on the analysis of \citet{2016MNRAS.455..357S}. The Baraffe et al.\ evolutionary models predict radii of 0.097--0.114~R$_{\odot}$ for these ages and the luminosity of {\shb}.

@@

\begin{deluxetable*}{lccccccccc}
\tablecaption{Observations\label{tab:obsParam}}
\tablewidth{0pt}
\tablehead{
 & \multicolumn{3}{c}{Observation Epoch (UT)} \\
 \cline{2-4}
\colhead{Target} & 
\colhead{Date} & 
\colhead{Start} & 
\colhead{End} & 
\colhead{$N_{int}$} & 
\colhead{$t_{int}$} & 
\colhead{Duration} & 
\colhead{Airmass} & 
\colhead{Reference Star} & 
\colhead{FWHM \@ $H$} \\
 & &  &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Start-End} & & \colhead{(\arcsec)}}
\startdata
{\sha} & 2015-12-31 & 09:35:10 & 14:14:22 & 352 & 60 & 7.47 & 1.59-1.28 & J08354383-0819212 & 0.5 \\
{\shb} & 2016-06-25 & 07:29:31 & 14:57:58 & 363 & 45 & 4.65 & 1.42-2.15 & J18212622+1414064 & 0.5 \\
\enddata
\tablecomments{N$_{int}$ is the number of integrations and t$_{int}$ is the effective integration time for the 32 non-destructive reads up the ramp. The duration is the total time from start to end of the observations including array sampling and overheads. The FWHM is the measured full width half maximum of the spatial point spread function around 1.6$\mu$m, taken as the median value over the entire time series.}
\end{deluxetable*}

@@

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
	\label{fig:specphot0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
	\label{fig:specphot1821}
	}
	\caption{Top Panels: Normalized median raw spectra of {\sha} (left) and {\shb} (right) in black, compared with the respective reference stars (blue) and background emission (red; mostly telluric OH emission and thermal background). The areas of higher telluric absorption are visible near 1.4~$\mu$m and 1.8~$\mu$m.  Bottom Panels: Dynamic spectra of each brown dwarf system. The dynamic spectrum for \sha\ shows no significant variability in the spatial or spectral direction whereas \shb\ shows significant modulations with a period near 4 hours.
The variability in \shb\ is prominent at the short wavelengths with a magnitude of $\sim$2--3\% peak-to-trough, but $\lesssim 0.5\%$ toward 2~$\mu$m.}
	\label{fig:specphot}
	\vspace{0.1in}
\end{figure*}

@@

\begin{figure*}[!t]
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
	\label{fig:tserPhase0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
	\label{fig:tserPhase1821}
	}
	\caption{Time series for each system, after subtraction of baseline trends. Each wavelength binned lightcurve is color coded, offset, and labeled on the right side. \sha\ shows relatively flat light curves whereas \shb\ has clearly visible double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.
	Lines trace the best double sinusoidal model fit for each light curve.
	Green brackets show regions where telluric absorption may contaminate the time series.}
	\label{fig:tserDetrend}
\end{figure*}

\begin{figure*}
\centering
\subfloat[2MASS J0835]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
	\label{fig:ampspec0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
	\label{fig:ampspec1821}
	}
	\caption{(Top panels) Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows only marginally significant variability near 1.7~$\micron$ and 2.1--2.4~$\micron$, and no obvious trends with wavelength. \shb\ has significant variability over wavelengths $<$1.7$\micron$ with a strong spectral slope.
	 Also shown is the WFC3 amplitude spectrum of \shb\ from \citet{2015ApJ...798L..13Y}. The WFC3 observations were obtained on a different epoch, but show a similar slope.
	 The amplitude spectrum for \shb\ is fit to a simple Mie scattering model with a log-normal particle size distribution of spherical forsterite grains; the best fit has a median particle size of 0.28 $\mu$m.
	 In all plots the regions potentially contaminated by telluric absorption are shaded in light green.
	 {\it Bottom Panels:} The time offset of maximum amplitude, $t_1$ (in hours), relative to the reference epoch (JD 2457388.0 for \sha\ and JD 2457565.0 for {\shb}).
	 Neither shows a clear trend with wavelength, indicating no significant phase offsets.
	 For wavelengths with small variability amplitudes, $t_1$ becomes as wide as the prior window $-\tau/2 < t_1 < \tau/2$.}
	\label{fig:ampSpec}
\end{figure*}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_a2_t2.pdf}
\caption{Secondary sinusoidal amplitude ($A_2$) as a function of wavelength for \shb.
As in Figure \ref{fig:ampSpec}, the regions potentially contaminated by telluric absorption are shown in green.
The secondary amplitude $A_2$ shows a gradual decrease as a function of wavelength, similar to that seen with $A_1$.
{\it Bottom Panel:} The time offset of maximum variation, $t_2$ (in hours) shows no clear phase shift trend.
The constraints approach the prior $\pm \tau$/4 when no significant variability is detected.
The $A_2$ constraints for \sha\ (not shown) are all consistent with zero.}\label{fig:amp2Spec}
\end{centering}
\end{figure}

@@

Figure \ref{fig:specphot} shows the raw spectra of the two brown dwarfs, their reference spectra and the background spectra.
Neither the reference spectra nor the brown dwarf spectra have any corrections applied for telluric absorption or instrumental spectral response.
The reference stars have significantly bluer spectra than the brown dwarfs, but nonetheless contain the same telluric water absorption signatures
near 1.37~$\mu$m and 1.83~$\mu$m, resulting in significantly lower flux.

Figure \ref{fig:specphot} also shows the dynamic spectra, the relative source brightness as a function of wavelength and time.
{\sha} has dynamic spectra resembling white noise, with no significant variations in either spectral or temporal axes at the $\lesssim$0.5\% level.
{\shb}, on the other hand, shows a clear periodic signal that is strongest at the shortest wavelengths and declines in amplitude toward the longest wavelengths. The periodic signal is nearly coincident with the 4.2~hr period measured by \citet{2015ApJ...799..154M}, enabling confirmation that the signal is astrophysical rather than systematic (see \citealt{2016ApJ...826..156S}).
Both sources exhibit some systematic features in the strong telluric absorption bands at 1.4 and 1.8~$\mu$m, likely caused by residual wavelength drifts from flexure and lower signals-to-noise.

@@

We find minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particularly in bands $<$1.8~$\mu$m. 
These variations are periodic with ``double-hump'' structures at peak amplitudes around -2.7~hr and +1.3~hr relative to JD 2457565.00.
The amplitude of these variations is strongly wavelength-dependent with $\sim$3.0\% peak-to-trough variations at short 
wavelengths and near-zero amplitude at the longest wavelengths.

Each of the raw light curves were fit to a double sinusoidal model:
\begin{equation}\label{eq:cosfit}
\begin{split}
F(t) = \left( A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + 1\right) \\
\times (B t + C + D a(t))
\end{split}
\end{equation}
where $F(t)$ is the relative flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two sinusoid terms, $t_1$ and $t_2$ are the time of maximum periodic flux for each sinusoid term, $\tau$ is period of the variations, $a(t)$ is the airmass as a function of time and $B$, $C$ and $D$ are constants quantifying baseline (i.e., non-astrophysical) trends.
Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
of 2.6 $< \tau < $3.6 hr for \sha]\ and 3.7 $< \tau <$ 4.7 hr for {\shb}, $\pm$0.5 hr around the literature values.
These priors are wide enough they don't drive the constraints on $\tau$ at short wavelengths for {\shb}, but narrow enough to ensure that the sinusoidal fits do not just fit the airmass trends with time.
We also restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ and $-\tau/4 < t_2 < \tau/4$ to assure there are no 2$\pi$ degeneracies in the fit.
We do not put any constraints on A$_1$ relative to A$_2$.

Figure \ref{fig:ampSpec} shows the MCMC posterior constraints for periodic amplitudes as a function of wavelength.
For {\sha} (Figure \ref{fig:ampspec0835}) we find at most small amplitude variability ($\lesssim 0.5\%$), marginally significant at 1.7~$\mu$m and 2.1--2.35~$\mu$m, with a flat trend as a function of wavelength.
\shb, on the other hand, shows highly significant variability with a decreasing trend in amplitude as function of wavelength.
In both cases, we find no statistically significant wavelength dependence on the time of maximum variation $t_1$, and hence no phase variation.
The period of \shb\ is found to be consistent with that of \citet{2015ApJ...799..154M}.
If we optimistically assume all wavelengths are statistically independent, the weighted average rotation period is 4.10 $\pm$ 0.03 hours.

Figure \ref{fig:amp2Spec} shows the posterior constraints on the secondary sinusoidal term.
As with $A_1$, the amplitude spectrum decreases as a function of wavelength, indicating Mie scattering grains and that the higher frequency term is likely just smaller scale cloud structures with similar properties as the longer timescale variability.
As with Figure \ref{fig:ampSpec}, we find no significant wavelength dependence on the time of maximum variation, $t_2$.

The same trend of decreasing variability amplitude for \shb\ was observed by HST's WFC3 grism over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{2015ApJ...798L..13Y}, shown in Figure \ref{fig:ampspec1821}.
The HST WFC3 maximum over minimum flux spectrum ($f_R$) is converted to an amplitude spectrum by assuming that the amplitude is half the difference in maximum and minimum flux, which can be shown to be 
\begin{equation}\label{eq:ampFromRatio}
A  = \frac{f_R - 1}{f_R + 1}
\end{equation}
There is a multiplicative offset of 25\% between the IRTF and WFC3 spectrum that may be due to different spatial cloud and temperature distributions  different epochs.
\citet{2015ApJ...798L..13Y} find that the WFC3 amplitude spectrum has no significant water vapor absorption which indicates a high haze layer in {\shb}. This is consistent with our gradually decreasing slope from 1.1 to 1.7~$\mu$m.

@@

\citet{hiranaka2016subMicronDust} find that the observed spectra of reddened L dwarfs can be explained by extinction from a haze layer of sub-micron forsterite grains.
They find typical mean particle radii of 0.15 to 0.35 $\mu$m for a sample of L dwarfs.
Our median particle radius of $r$=0.24$^{+0.05}_{-0.07}$~$\mu$m for \shb\ is consistent with this range and may represent a partially cloudy version of the reddened brown dwarfs in \citet{hiranaka2016subMicronDust} or of WISEP J0047+6803.
